intRo

### 2015-01-09 presentations/departmental-seminar/index.Rmd
updates from @dicook

 - `R` is great, but requires students to have some knowledge/interest in programming
 - JMP is powerful, but confusing to students
      - Licenses
      - Inconsistent UI
 - Students fight with software rather than focusing on the goal: statistics

## What is `intRo`?
 - A modern **web-based** application for performing basic data analysis and statistical routines
 - Built using `R` and `Shiny`
 - Powerful and extensible modular structure
 - Simple enough for the novice statistician
 - Assists in the learning of statistics rather than acting as a stand-alone deliverer of statistics education

@@

## `intRo` in the wild
 - `intRo` is currently being used in STAT 201
      - Homework assignments and labs will use `intRo` to emphasize class concepts
 - `intRo` is a supplement, not the focus of the class

>>>>

 - `R` is great, but requires students to have some knowledge/interest in programming
 - JMP is powerful, but too big
      - Licenses
      - Inconsistent UI
 - Want students to focus on data analysis rather than fight with software

## What is `intRo`?
 - A simple **web-based** application for performing basic data analysis and statistical routines
 - Built using `R` and `Shiny`
 - Extensible modular structure
 - Designed for a first statistics class student
 - Assists in the learning of statistics rather than acting as a stand-alone deliverer of statistics education

@@

## `intRo` in the wild
 - `intRo` will be used this semester in STAT 201
      - Homework assignments and labs will use `intRo` to emphasize class concepts
 - `intRo` is a supplement, not the focus of the class
